Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-26 astronum_2018/astronum-xrb.tex
updated fig

Figure~\ref{fig:xrb} \MarginPar{Mike will update this}

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{xrb}
\caption{\label{fig:xrb} Helium flame spreading across the surface of
  a neutron star.  Shown are temperature (top), the velocity out of the
  simulation plane (middle), and nuclear energy generation rate
  (bottom).
  The out of plane velocity contours indicate where the Coriolis force
  has created a hurricane-like wind structure which confines the flame,
  leading to an inclined front. It is at such an interface that the
  temperature and burning rate are highest.
  }
\end{figure}

@@

Other ways to make the simulation less expensive can include a subgrid model,
even something as simple as subzone burning.\MarginPar{need the paper ref fo rthis}
This is harder...

>>>>

Figure~\ref{fig:xrb} shows the flame structure.  The top panel shows
the temperature.  The initial perturbation reached to $2\times
10^4~\mathrm{cm}$, so at this point, the extend of the burnt region
has nearly doubled.  The flame structure is quite wide

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{xrb}
\caption{\label{fig:xrb} Helium flame spreading across the surface of
  a neutron star.  Shown are temperature (top), the velocity out of the
  simulation plane (middle), and nuclear energy generation rate
  (bottom).
  The out of plane velocity contours indicate where the Coriolis force
  has created a hurricane-like wind structure which confines the flame,
  leading to an inclined front. It is at such an interface that the
  temperature and burning rate are highest.
  }
\end{figure}

@@

Other ways to make the simulation less expensive can include a subgrid
model, Flame models are commonly used for Type Ia supernovae.  There
however, the flame is thin compared to the scale height, so a simple
model can represent the unresolved flame on the grid.  For the XRB,
the flame thickness is a non-trivial fraction of the pressure scale
height and further, the laminar flame properties will change strongly
over the height of the burning layer (see~\cite{Timmes00}).  This
makes traditional flame models a poor fit.  Methods that use even
something as simple as subzone burning.  This is harder...
